\documentclass[11pt]{amsart}
\usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   % ... or a4paper or a5paper or ... 
%\geometry{landscape}                % Activate for for rotated page geometry
%\usepackage[parfill]{parskip}    % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{epstopdf}
\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}

\title{Peer review form}

\begin{document}
\maketitle

%First sentence of reviewed report: 

\subsection*{Overall assessment}
\ \bigskip

% Put one cross "X" in each row 

\begin{center}
  \begin{tabular}{|p{5cm}|c|c|c|} 
     \hline
     & weak & satisfactory & strong \\ \hline 
     Contents {\footnotesize \begin{itemize} \item covering \item relevance \end{itemize}} & &X & \\ \hline 
     Presentation {\footnotesize \begin{itemize} \item guiding the reader \item flow of ideas \item type-setting and spelling \end{itemize}} & X& & \\ \hline 
     Evidence {\footnotesize \begin{itemize} \item credibility \item correctness \end{itemize}} & &X & \\ \hline 
     Overall effectiveness & &X & \\ \hline 
  \end{tabular}
\end{center}

In general, it is a satisfactory work, considering it is done by a single person.
\subsection*{Specific comments on contents}

% Write your comments here

\begin{itemize}
	\item The content covers all aspects to be discussed in a concise way.
	\item The theoritical part (Problem 1 \& 2)is self-contained with detailed derivation.
	\item The code part (Problem 3,4 \& 5) only focuses on the result, but does not give any illstration on how to get it or why.
\end{itemize}

\subsection*{Specific comments on presentation}

% Write your comments here
\begin{itemize}
	\item The report is organized by simply giving answers to problems, however, doesn't show the flow of ideas between problems.
	\item As has been commented, the code part (Problem 3,4 \& 5) is lack of detailed illstration, therefore, is far from understandable without access to the code.
	\item The code should be more organized and needs more comments. 
\end{itemize}

\subsection*{Specific comments on evidence}

% Write your comments here
\begin{itemize}
	\item The result is okay in general, both the theoritical part and the code part.
	\item To be improved, in the maximum likelihood estimation of $\varsigma$, the step size $0.2$ is too large, and should be narrowed to $0.05$ or even lower. If there is problem about computing time, it can be first limited to a certain  interval and obtained in a progressive way.
\end{itemize}
\end{document}  